Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Removed results for profile at SUP.

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
        \subcaption{
            Standard User Position.
            Concentric white circles indicate nominal umbra and penumbra limits.
        }
        \label{fig:SUPDensity}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
        \subcaption{Close User Position}
        \label{fig:CUPDensity}
    \end{minipage}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP.
        \SI{10.2}{\cm} diameter collimator.
    }
    \label{fig:SUPDensity}
\end{figure}

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofie14}.
The parameterisation therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.

Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{SUP10beamproFoldingRADECS.png}
    \caption{
        Neutron profile at the SUP, normalised to fluence rate on axis.
        Vertical lines indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPProfile}
\end{figure}

@@

Fig.~\ref{fig:CUPDensity} and Fig.~\ref{fig:CUPProfile} show neutron spatial distribution (for neutrons above \SI{10}{\MeV}) and profile (folded in energy with the \U238\ fission cross-section) at the CUP.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
    \caption{Spatial distribution of neutrons above \SI{10}{\MeV} at the CUP}
    \label{fig:CUPDensity}
    \todo{Show density of neutrons above \SI{10}{\MeV} at CUP}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{Neutron profile at the CUP}
    \label{fig:CUPProfile}
    \todo{Show CUP profile, compared to measurements}
\end{figure}

>>>>

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
        \subcaption{
            Standard User Position.
            Concentric white circles indicate nominal umbra and penumbra limits.
        }
        \label{fig:SUPDensity}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
        \subcaption{Close User Position}
        \label{fig:CUPDensity}
    \end{minipage}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP.
        \SI{10.2}{\cm} diameter collimator.
    }
\end{figure}

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev14}.
The parameterisation therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP and SUP}

Fig.~\ref{fig:CUPProfile} shows neutron fluence profile at the CUP, compared with measurements.
In Fig.~\ref{fig:CUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating the measurements which were made with a \U238\ TFBC~\cite{Prokofiev2009}.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{CUPTOF10beamproRADECS.png}
    \caption{Neutron profile at the CUP, normalised to fluence rate on axis.}
    \label{fig:CUPProfile}
\end{figure}

@@
